Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/type-theory.tex
Cosmetic changes.

\begin{notation}
  Types are written using \abbre{small caps}.  We write the type
  judgments as $a : \abbre{a}$ to denote that~$a$ is of
  type~$\abbre{a}$.
\end{notation}

@@

\begin{notation}

We use \Prop for the type of propositions.
For syntactical equivalence, we write the equality as $φ ≡ ψ$
for $φ,~ψ : \Prop$. For this equality, we assume the
reflexivity, symmetry and transitivity properties.

\end{notation}

\begin{notation}

The type of natural numbers is called \Nat, and it is defined as
usual, where $\zero$ and $\suc$ are its data constructors. We use names
and symbols for the arithmetic operations as usual ($+$, $-$, $*$).
We include syntax sugar for $\zero$, $\suc$, $\suc~\zero$,
$\cdots$, with the decimal representation: $0$, $1$, $2$, $\cdots$
as well.

\end{notation}

>>>>

\begin{notation}
  Types are written using \abbre{small caps}.  We write the type
  judgments as $a : \abbre{a}$ to denote that the term~$a$ is of
  type~$\abbre{a}$.
\end{notation}

@@

\begin{notation}
  We use \Prop for the type of propositions.  For syntactical
  equivalence, we write the equality as $φ ≡ ψ$ for $φ,~ψ :
  \Prop$. For this equality, we assume the reflexivity, symmetry and
  transitivity properties. The type of natural numbers is called \Nat,
  and it is defined as usual, where $\zero$ and $\suc$ are its data
  constructors. We use names and symbols for the arithmetic operations
  as usual ($+$, $-$, $*$).  We use syntax sugar for $\zero$, $\suc$,
  $\suc~\zero$, $\dots$, with the decimal representation~$0$, $1$,
  $2$, $\dots$ as well.
\end{notation}
